\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{1pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item\vspace{1pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\fontsize{3}{3}\selectfont$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[font=\footnotesize, itemsep=2pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Huge \scshape Frank Laterza} \\
    \small 941-223-5298 $|$ \href{mailto:franklaterza@gmail.com}{\underline{franklaterza@gmail.com}} $|$ 
    \href{https://franklaterza.com}{\underline{franklaterza.com}} $|$ 
    \href{https://github.com/franklaterza}{\underline{github.com/franklaterza}} $|$ 
    \href{https://linkedin.com/in/laterzafrank/}{\underline{linkedin.com/in/laterzafrank}} \\
    \vspace{-2pt}
    Embedded Software Engineer $\cdot$ UCF Computer Engineering Student
\end{center}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Central Florida}{Orlando, FL}
      {Bachelor of Science in Computer Engineering}{Expected Graduation: Dec. 2025}
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Rust, Python, Java, TypeScript, Next.js, VHDL, Verilog, GNU/Linux, Git, OOP, Data Structures} \\
     \textbf{Hardware/Tools}{: Embedded Systems, FPGA, Eagle CAD, SolidWorks, Fusion 360, Lathe, CNC, Soldering, SMT/THT} \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Apple}{Cupertino, CA}
      {Software Engineer Intern}{May 2025 -- Aug. 2025}
      \resumeItemListStart
        \item{Prototyped first party feature for the Apple HomePod integrated into app}
        \item{Modified Percies Time Protocol algorythm for timing syncronisation across home devices creating lightweight}
        \item{Archited software designed for distruputed systems in a home environment}
      \resumeItemListEnd

    \resumeSubheading
      {NVIDIA}{Santa Clara, CA}
      {GPU Firmware Engineer Intern}{May 2024 -- Aug. 2024}
      \resumeItemListStart
        \item{Refactored security key signing software for dynamic metadata parsing allowing clients to securely update firmware images}
        \item{Contributed to GPU BIOS build system for stack analysis resulting in prevention of unknown stack overflow errors.}
        \item{Released client facing tools exposing I2C event logs and faults to diagnose crashes for enterprise datacenter GPUs.}
      \resumeItemListEnd

    \resumeSubheading
      {Eta Space}{Rockledge, FL}
      {Software Engineer Lead}{June 2023 -- Current}
      \resumeItemListStart
        \item{Lead software development for NASA funded satellite mission designed to demonstrate lossless cryogenic liquid transfer.}
        \item{Leveraged multithreading to design software for flight computer to record scientific measurements and control external hardware.}
        \item{Archited software design for Orbital mission execution for redundant, fault tollerent system}
        \item{Designed PCB and Software allowing reprogram during flight }
        \item{Implemented fully encrypted packet telemetry system for critical mission data integrated with Rocket Lab Space Craft}
        \item{Designed UI for testing and lab use to help engineers interface with flight computer}
        \item{Developed software for embedded system stack designed to control sensors, heaters, and valves, and pressure transducers.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Central Florida's CREOL College of Optics and Photonics}{Orlando, FL}
      {Undergraduate Research Assistant}{Jan. 2023 -- May 2023}
      \resumeItemListStart
        \item{Developed VHDL software for measurement of arrival of photons utilizing FPGA.}
        \item{Verified accuracy through simulation using ModelSim, resulting in 4 times the performance using timing techniques.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeSubheading
        {S.P.U.D (Custom RISC-V CPU) }{Aug. 2025}
        { C, MultiSim, }{}
        \resumeItemListStart
          \item{Customized 5 stage pipeline RISC-V 32bit CPU designed drive 64x64 RGB-LED display and run games written in C}
          \item{Designed custom display driver logic using protected ram buffers allocated for colored pixel values for RGB-LED Matrix} 
          \item{Developed the S.P.U.D SDK for interfacing with hardware and graphics engine. TODO FILL} 
        \resumeItemListEnd
      \resumeSubheading
        {Dex (Self-Balancing Robot)}{Dec. 2024}
        {C/C++, Fusion 360, Eagle Cad}{}
        \resumeItemListStart
          \item{Created an open-source self-balancing robot controlled over Bluetooth using Pico SDK, FreeRTOS Kernel, and BTstack.}
          \item{Leveraged multicore real time embedded software using FreeRTOS to process controls, gather sensor data, and drive motors.}
          \item{Implemented robust and responsive control system responsible for balancing through a real time feedback loop using gyroscope.}
          \item{Designed moduler PCB for microcontroller, gryoscope/accelerometer sensors, motor drivers, debugging, and battery management }
        \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}
